Cache is King: Presenting a Suite of Fast, Correlation Function Codes

### 2015-01-21 paper/ms.tex
The C link line was required
Updated the paper structure + some text

%%% Definitions added by Manodeep 
\newcommand{\Msun}{M_{\odot}}
\newcommand{\hMsun}{h^{-1}M_{\odot}}
\newcommand{\sdss}{{\small{SDSS}}\xspace}
\newcommand{\hMpc}{\ensuremath{{h^{-1}Mpc}\xspace}}
\newcommand{\hkpc}{\ensuremath{{h^{-1}kpc}\xspace}}
\newcommand{\rmax}{\ensuremath{{r_{max}}}\xspace}
\newcommand{\todo}[1]{\marginpar{TODO}{\color{red}#1}}

\lstset{
  language=C,                % choose the language of the code
  numbers=left,                   % where to put the line-numbers
  stepnumber=1,                   % the step between two line-numbers.
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
  title=\lstname,                 % show the filename of files included with \lstinputlisting;
}

@@

%% \begin{lstlisting}
%% \end{lstlisting}

%% \lstinputlisting{cellarray.h}

%% \footnote{Most of the code assumes that the number of galaxies is within INT_MAX $\sim$ 2.1 billion. So, it would appear 
%% to make no sense that the field inside the struct cell has `nelements' of type \verbatim{int64_t}. The reason I have 
%% chosen to use \verbatim{int64_t} is that under C alignment rules 4 bytes of padding would have appended anyway to the struct cell. So, I chose 
%% to declare `nelements' as an \verbatim{int64_t} and used those 4 bytes. Saves some future conversion/coding. }

@@

\subsection{Comparison to Tree Algorithms}

\section{Results}

\section{Benchmarks \& Scaling}

>>>>

%%% Definitions added by Manodeep 
\newcommand{\Msun}{M_{\odot}}
\newcommand{\hMsun}{h^{-1}M_{\odot}}
\newcommand{\sdss}{{\small{SDSS}}\xspace}
\newcommand{\hMpc}{\ensuremath{{h^{-1}Mpc}\xspace}}
\newcommand{\hkpc}{\ensuremath{{h^{-1}kpc}\xspace}}
\newcommand{\emcee}{\texttt emcee}
\newcommand{\rmax}{\ensuremath{{r_{max}}}\xspace}
\newcommand{\xir}{\ensuremath{{\xi(r)}}\xspace}
\newcommand{\wprp}{\ensuremath{{w_p(r_p)}}\xspace}
\newcommand{\xirppi}{\ensuremath{{\xi(r_p,\pi)}}\xspace}
\newcommand{\todo}[1]{\marginpar{TODO}{\color{red}#1}}

\lstset{
  language=C,                % choose the language of the code
  numbers=left,                   % where to put the line-numbers
  stepnumber=1,                   % the step between two line-numbers.
  numbersep=10pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
}

@@

\lstinputlisting[firstline=11]{../xi_theory/include/cellarray.h}

Since the typical particle data is small ($\sim$ 20-30 MB), duplicating the entire particle distribution does not impose a strong 
constraint on the memory requirements. However, this duplication allows us to store the particles contiguously and produces fewer 
cache misses while looping over particles in a cell. 
The entire 3-D particle distribution is then deposited on the uniform grid. Now, for each particle we need to visit 27 total cells to 
compute all possible pairs within \rmax.

\section{The pair-counting algorithm}

\subsection{\xir}
\subsection{\xirppi}
\subsection{\wprp}

@@

\section{Benchmarks \& Scaling}
In this section we present the runtimes and OpenMP scaling for the different codes.

\subsection{\xir}
\subsection{\xirppi}
\subsection{\wprp}
